Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-12-17 slides/ExpSlides.tex
slides for brown bag seminar. Will work on following things. 1. true GMM, unconditional moments. 2. randseed lead to SMM.

\documentclass{beamer}
\usepackage{default}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{adjustbox}  % Allows for fitting tables into slide

%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\title{Understanding Expectation Formation from Probabilistic Surveys}

@@

\date{April, 2019}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

@@

%\begin{frame}{Why studying expectation}
%\begin{itemize}
%	\item Both theories and empirical evidence on deviation from full-information rational expectation(FIRE)
%	\item ``Sluggish'' macro: i.e. ``excessive smoothing'' in consumption, sticky price adjustment by firms and UIP puzzle, forward guidance puzzle, etc
%	\item Heterogeneity in expectation matters for asset pricing
%	\item From \textcolor{blue}{revealed preference(belief)} to \textcolor{blue}{elicited beliefs}  	
%\end{itemize}
%\end{frame}

\begin{frame}{What I am doing}
\begin{itemize}
	\item Use \textcolor{blue}{density information} to 
	\begin{itemize}
		\item test expectation rigidity models 
		\item ... and identify differences in various theories 
	\end{itemize}
	\item Both \textcolor{blue}{individual} and population moments 
	\item \textcolor{blue}{Households} and professional forecasters 
	\begin{itemize}
		\item drivers of difference in rigidity across two types of agents
	\end{itemize}
	%\item Focus on aggregate variable inflation first, and then try \textcolor{blue}{individual variables} 
\end{itemize}
\end{frame}

\begin{frame}{Why density is important}
\begin{itemize}
\item \textbf{Identification:} different theories have testable predictions on the second moments   
	\begin{itemize}
		\item Scenario 1. Two people think the chance of raining is 50\%. 
		\item Scenario 2. One person thinks 100\% and the other 0\%. 
	\end{itemize}
\item \textbf{Modeling Implications:}  both mean and variance affect economic decisions
\begin{itemize}
	\item precautionary saving with income risks
	\item portfolio choice with risky asset
\end{itemize} 
\end{itemize}
\end{frame}

%
%\begin{frame}{Objections}
%\begin{itemize}
%	\item ``Subjective surveys are not trustworthy'' 
%	\begin{itemize}
%		\item Actually carefully designed. \cite{armantier2017overview}
%	\end{itemize}
%	\item ``People are bad at answering surveys, and worse on probabilities''  
%	\begin{itemize}
%		\item Not that bad. \cite{manski2004measuring}, \cite{delavande2014probabilistic}
%		\item Better than not.
%	\end{itemize}
%	\item ``A single parameter is enough for matching macro dynamics''
%	\begin{itemize}
%		\item No, heterogeneity in expectation could interact with other characteristics. 
%	\end{itemize}
%\end{itemize}
%\end{frame}

\begin{frame}{Literature}
\begin{itemize}
	\item \textbf{Theory}
	\begin{itemize}
		\item Sticky expectation \cite{carroll2003macroeconomic}, \cite{reis2006inattentive}
		\item Rational inattention \cite{sims2003implications},  \cite{gabaix2014sparsity}
		\item Noisy information \cite{lucas1972expectations}, \cite{woodford2001imperfect}
	\item Learning \cite{evans2012learning}
	\item Strategic interaction \cite{morris2002social}, \cite{hellwig2009knowing}
	\item Diagostic expectation  \cite{bordalo2018diagnostic}
	\item Model uncertainty \cite{hansen2001robust}, \cite{hansen2008robustness}
	\end{itemize}
\item \textbf{Empirics}
\begin{itemize}
	\item \textbf{Heterogeneity in Expectation:} \cite{mankiw2003disagreement}
	\item \textbf{Testing Theories:}  \textcolor{blue}{\cite{coibion2012can}, \cite{fuhrer2018intrinsic}}
\end{itemize}
\end{itemize}
\end{frame}

\section{Theories}

\begin{frame}{Unified Framework}

@@

\begin{eqnarray*}
	\widehat f_{i,t}(y_{t+h}|I_{i,t})
\end{eqnarray*}

\begin{itemize}
	\item Theories differ in $I_{i,t}$
	\item May also differ on information processing, i.e. $I_{i,t} \rightarrow \widehat f_{i,t}$
\end{itemize}

@@

\begin{frame}{Definition and notation}
\begin{itemize}
	\item \textcolor{red}{Individual}
	\begin{itemize}
		\item  mean forecast $\quad E_{i,t}(y_{t+h})$
		\item forecast error $\quad FE_{i,t+h|t} = y_{t+h}- E_{i,t}(y_{t+h})$
		\item \textcolor{blue}{uncertainty} $\quad Var_{i,t}(y_{t+h})$
	\end{itemize}
	\item \textcolor{red}{Population}
	\begin{itemize}
		\item average forecast  $\quad \bar E_{t}(y_{t+h})$
		\item average forecast error $\quad \overline {FE}_{t}= y_{t+h}-\bar E_{t}(y_{t+h})$
		\item \textcolor{blue}{cross-section disagreements}  $\quad Var_t(E_{i,t}(y_{t+h}))$
		\item \textcolor{blue}{average uncertainty}  $\quad \overline{Var}_t(y_{t+h})$
	\end{itemize}
\end{itemize}

@@

\begin{frame}{Assumption about true process}

$$y_{t+1} = \rho y_t + \omega_t  $$ 
$$\omega_t \sim N(0,\sigma^2_{\omega})$$

\begin{itemize}
	\item $0 < \rho \leq 1$
	\item if $\rho =0$, no way to forecast at all
	\item $\omega_t$ is i.i.d 
\end{itemize}

@@

\subsection{Sticky Expectation}

\begin{frame}{Sticky Expectation: assumptions}
\begin{itemize}
	\item At time $t$, agent $i$ learns about $y_t$ at a fixed Poisson rate $\lambda$ 
	\item A non-updater since $t-\tau$  
	$$E_{i,t}(y_{t+h}|y_{t-\tau}) =\rho^{h+\tau} y_{t-\tau} $$
	\item An updater is a special cae  $\tau=0$ 
\end{itemize}
\end{frame}

\begin{frame}{Impulse responses to shocks: individual moments}

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$ 
\begin{figure}
	\includegraphics[scale=0.25]{figures/ir_indse} 
\end{figure}
\end{frame}

\begin{frame}{Impulse responses to shocks: population moments}

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$

\begin{figure}
	\includegraphics[scale=0.25]{figures/ir_popse} 
\end{figure}

@@

\subsection{Other theories}

\begin{frame}{Noisy Information: assumptions}
\begin{itemize}
	\item Individual only observes noisy signals 
	\begin{eqnarray*}
		\begin{aligned}
			& s_{i,t}=[s^{pb}_t, s^{pr}_{i,t}]' \in I_{i,t} \\
			&\text{public signal:} \quad s^{pb}_t = y_t + \epsilon_t, \quad \epsilon_t \sim N(0,\sigma^2_\epsilon)\\ 
			& \text{private signal:} \quad s^{pr}_{i,t} = y_t + \xi_{i,t} \quad \xi_{i,t} \sim N(0,\sigma^2_\xi)
		\end{aligned}
	\end{eqnarray*}

	\item Kalman filtering (simply normal updating if $\rho$=0)
\end{itemize}
\end{frame}

\begin{frame}{Impulse responses to shocks: individual moments}

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figures/ir_indseni} 
\end{figure}

@@

\begin{frame}{Impulse responses to shocks: population moments}

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figures/ir_popseni} 
\end{figure}

@@

%\begin{frame}{Noisy Information: predictions}
%\begin{itemize}
%	\item \textbf{Similar to Sticky Expectation}
%	\begin{enumerate}
%\item \textbf{Macro rigidity}: population forecasts partially respond to shocks
% \item \textbf{Non-response of variance}: both individual and population variance \textcolor{blue}{does not respond to} shocks.   
% \end{enumerate}
%\item \textbf{Different from Sticky Expectation}

%	\begin{enumerate}
%	\item \textbf{Micro rigidity}: both individual and population forecast \textcolor{blue}{partially} respond to shocks 
%	\item \textbf{Horizon-sensitive rigidity}: rigidity decreases with horizon
%	\item \textbf{Increasing disagreements:} population disagreements \textcolor{blue}{increase} over time as approaching $t+h$
%	\item \textbf{Shock-specific responses:} different impacts of fundamental shocks, or simply news shocks 
%\end{enumerate}
%\end{itemize}

%\end{frame}

\begin{frame}{A detailed look into noisy information}

\begin{figure}
	\includegraphics[height=8cm,width=8cm]{figures/ni_illustration} 
\end{figure}

\begin{frame}{Implied rigidity of different models}

\begin{figure}
	\includegraphics[height=5cm,width=8cm]{figures/rigidity} 
\end{figure}

\begin{frame}{Other theories on to-do-list}
\begin{itemize}
	\item \textbf{Rational Inattention:} attentiveness endogenously respond to variances
	\item \textbf{Learning}: the structural parameter $\rho$ is not known, thus the agent learns about it as if an econometrician does
\end{itemize}
\end{frame}

\begin{frame}{Identification strategies 1: testing rigidity models}

\begin{itemize}
	\item\cite{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} respond to shocks and serially correlated. 
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} does not depend on shocks; and serially correlated. 
	\end{itemize}
\end{itemize}

\begin{frame}{Identification strategies 2: differentiating theories}
\begin{itemize}
	\item\cite{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} do not depend on past realizations according to baseline SE and NI; but do so according to heterogeneous priors or precision models. 
		\item Implied rigidity does not differ across shocks according to SE but differs according to NI. 
		\item \textcolor{blue}{Disagreements} rise after shocks according to baseline SE, strategic interactions and heterogeneous priors but invariant according to baseline NI.
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} do not depend on shocks per se according to baseline SE and NI, instead on degree of information rigidity.
	\end{itemize}
\end{itemize}

\section{Data and Methodology}

		\hline 
		& SCE & SPF        \\
		\hline 
		Time period                                    & 2013-present                            & 2007-present             \\
		Frequency                                      & Monthly                                 & Quarterly                \\
		Sample Size                                    & 1,300                                   & 30-50                    \\
		Aggregate Var in Density                       & \textcolor{blue}{1-yr and 3-yr inflation}          & \textcolor{blue}{1-yr and 3-yr CPI and PCE}         \\
		Pannel Structure                               & stay up to 12 months                    & average stay for 5 years \\
		Demographic Info                        & Education, Income, Age        & Industry    \\
		\hline 
	\end{tabular}}
\end{table}

\section{Stylized Facts}

\begin{frame}{Population moments: average}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_med.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average forecast errors}
\begin{figure}
	\includegraphics[scale=0.3]{figures/fe_fe.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average uncertainty}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_var.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average uncertainty}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_var.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/disg_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_disg2.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: forecast and realization}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_true.png} 
\end{figure}
\end{frame}

\section{Empirical Results}

\begin{frame}{Empirical execution}

\item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
 \item \textbf{Identification of Shocks}: following \cite{coibion2012can} and monetary policy shocks. 
\end{itemize}

\subsection{Test of Null Hypothesis of Rational Expectation}

>>>>

\documentclass{beamer}
\usepackage{default}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{adjustbox}  % Allows for fitting tables into slide
\usepackage{hyperref}
\usepackage{threeparttable}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{natbib}
\usepackage{adjustbox}
\usepackage{subcaption}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\title{Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households}

@@

\date{\today}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

@@

\begin{frame}{Motivation}
	\begin{itemize}
		\item there are various theories on  ``irrational expectation''
		\item different theories can be tested using survey data  in a comparable manner  (\citet{coibion2012can})
		\item a good theory needs to be (relatively) consistent in predictions across different moments
		\item higher moments, i.e. uncertainty, brings about one more restriction
		\item survey also contains information about data generating process itself
	\end{itemize}
\end{frame}

\begin{frame}{What this paper does}
	\begin{enumerate}
		\item time series and cross-sectional pattern of \textcolor{blue}{uncertainty} from \textbf{density} forecasts of the inflation 
		\item additional reduced-form tests of the full-information rationality null using the uncertainty 
		\item extend \citet{coibion2012can} in two ways 
		\begin{itemize}
		\item cross-moment estimation for each one of the particular theories on expectation 
		\item allowing for stochastic volatility of inflation process 
		\end{itemize}
	\end{enumerate}
\end{frame}

\begin{frame}{Literature}
\begin{itemize}
	\item empirical tests on expectation formation
	\begin{itemize}
		\item \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}, \citet{malmendier2015learning}, \citet{das2017socioeconomic}, \citet{coibion2012can}, \citet{fuhrer2018intrinsic} 
	\end{itemize}
    \item density and probabilistic questions in expectation surveys
    \begin{itemize}
    	\item  \citet{manski2004measuring}, \citet{delavande2011measuring}, \citet{manski2018survey} 
    	\item  \citet{bertrand2001people},  \citet{van2008rethinking},  \citet{delavande2014probabilistic}
    \end{itemize}
    \item different measures of uncertainty
    \begin{itemize}
    	\item \citet{bachmann2013uncertainty},  \citet{jurado2015measuring}, \citet{binder2017measuring},  \citet{bloom2009impact}
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{A generic framework}

@@

	\begin{eqnarray*}
		f_{i,t+h|t} \equiv f_{i,t}(y_{t+h}|I_{i,t})
	\end{eqnarray*}

	\begin{itemize}
		\item theories of expectation differ in $I_{i,t}$ 
		\begin{itemize}
			\item rational expectation (FIRE): $I_{i,t} = y_{i,t}$
			\item sticky expectation (SE):  $I_{i,t} = y_{t-\tau}$, $\tau$ being the most recent update date
			\item noisy information (NI): $I_{i,t} = s_{i,t}(y_t)$, where $s_{i,t}$ is a vector of noisy signal(s)
		\end{itemize}
		\item the process of variable determines the mapping from $I_{i,t}$ to $f_{i,t+h|t}$
	\end{itemize}
\end{frame}

\begin{frame}{Definition and notation}
	\begin{table}[ht]
		\centering
		\label{MomSum}
		\begin{tabular}{ll}

			\hline 
			Individual moments                                  & Population moments                             \\
			\hline 
			Mean forecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
			Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
			Uncertainty: $Var_{i,t+h|t}$         & \textbf{Average uncertainty}:  $\overline{Var}_{t+h|t}$ \\
			& Disagreement:  $\overline{Disg}_{t+h|t}$       \\
			\hline 
		\end{tabular}
	\end{table}

@@

				\hline 
				& SCE & SPF        \\
				\hline 
				Time period                                    & 2013M6-2018M6                            & 2007Q1-2018Q4             \\
				Frequency                                      & Monthly                                 & Quarterly                \\
				Sample Size                                    & 1,300                                   & 30-50                    \\
				Aggregate Var in Density                       & \textcolor{blue}{1-yr-ahead inflation}          & \textcolor{blue}{1-yr and 3-yr core CPI and core PCE}         \\
				Pannel Structure                               & stay up to 12 months                    & average stay for 5 years \\
				Demographic Info                        & Education, Income, Age        & Industry    \\
				\hline 
		\end{tabular}}
	\end{table}
\begin{itemize}
	\item density estimation following (\citet{engelberg2009comparing})
	\item exclude top and bottom 5\% values for forecast errors and uncertainty
\end{itemize}
\end{frame}

\begin{frame}{Basic patterns: uncertainty and realized inflation}
	\begin{figure}
		\centering
		\label{InfVar}
		\includegraphics[width=0.3\textwidth]{figuresDraft/Inf1yf_CPIAU_varSPFCPIQ.png}
		\includegraphics[width=0.3\textwidth]{figuresDraft/Inf1yf_PCE_varSPFPCEQ.png}
		\includegraphics[width=0.3\textwidth]{figuresDraft/Inf1yf_CPIAU_varSCEM.png}
	\end{figure}

@@

\begin{frame}{Basic patterns: uncertainty and the size of forecast errors}
	\begin{figure}
		\centering
		\label{FEVar}
		\includegraphics[width=0.3\textwidth]{figuresDraft/SPFCPI_abFE_varSPFCPIQ.png}
		\includegraphics[width=0.3\textwidth]{figuresDraft/SPFPCE_abFE_varSPFPCEQ.png}
		\includegraphics[width=0.3\textwidth]{figuresDraft/SCE_abFE_varSCEM.png}
	\end{figure}
\begin{itemize}
\item no evidence for positive correlation betwen high ex ante uncertainty and ex post forecast errors.
\end{itemize}
\end{frame}

\begin{frame}{Basic patterns: uncertainty and disagreement}
	\begin{figure}
		\centering
		\label{DisgVar}
		\includegraphics[width=0.3\textwidth]{figuresDraft/CPI_disg_varSPFCPIQ.png}
		\includegraphics[width=0.3\textwidth]{figuresDraft/PCE_disg_varSPFPCEQ.png}
		\includegraphics[width=0.3\textwidth]{figuresDraft/Q9_disg_varSCEM.png}
	\end{figure}
\begin{itemize}
	\item uncertainty are not the same as disagreement for professionals 
\end{itemize}
\end{frame}

\begin{frame}{Basic patterns: summary}
	\begin{itemize}
		\item uncertainty varies across time 
		\item uncertainty contains different information from widely  proxies such as disagreement and forecast error
	\end{itemize}
\end{frame}

\section{Theory}

\begin{frame}{AR(1) model of inflation}

\item 	\textbf{Inflation process}	
	$$y_{t} = \rho y_{t-1} + \omega_t  $$ 
	$$\omega_t \sim N(0,\sigma^2_{\omega})$$

\item \textbf{Uncertainty}
		\begin{itemize}
			\item FIRE: time-invariant 
			\begin{eqnarray*}\label{VarREPop}
				\overline{Var}^*_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}
			\end{eqnarray*}

			\item SE: time-invariant 
			\begin{eqnarray*}\label{VarSEPopRE}
				\overline{Var}^{se}_{t+h|t} = \sum^{+\infty}_{\tau =0} \lambda (1-\lambda)^\tau \overline{Var}^*_{t+h|t-\tau}
			\end{eqnarray*}

			\item NI: time-variant but quantitatively tiny due to highly efficient Kalman gain

			\begin{eqnarray*}\label{VarNIPopRE}
				\overline{Var}^{ni}_{t+h|t} = \rho^{2h} \overline{Var}^{ni}_{t|t} + \overline{Var}^*_{t+h|t}
			\end{eqnarray*}
		\end{itemize}

@@

\begin{frame}{Stocastic volatility (UCSV) inflation process (\citet{stock2007has})}

\begin{itemize}
\item \textbf{Inflation process}
\begin{eqnarray*}
\begin{split}
& y_t = \theta_t + \eta_t,\quad \textrm{where } \eta_t =\sigma_{\eta,t} \xi_{\eta,t} \\
& \theta_t = \theta_{t-1} + \epsilon_t, \quad \textrm{where }  \epsilon_t =\sigma_{\epsilon,t} \xi_{\epsilon,t} \\
& \log\sigma^2_{\eta,t} = \log\sigma^2_{\eta,t-1} + \mu_{\eta,t} \\
& \log\sigma^2_{\epsilon,t} = \log\sigma^2_{\epsilon,t-1} + \mu_{\epsilon,t} 
\end{split}
\end{eqnarray*}

\begin{eqnarray*}
\begin{split}
& \xi_t =[\xi_{\eta,t},\xi_{\epsilon,t}] \sim N(0,I_2) \\
& \mu_{t} = [\mu_{\eta,t},\mu_{\epsilon,t}]' \sim N(0,\gamma I_2) 
\end{split}
\end{eqnarray*}
\end{itemize}

@@

\begin{frame}{UCSV inflation process}

	\begin{itemize}
		\item \textbf{Uncertainty}
		\begin{itemize}
			\item FIRE: time-varying  \begin{eqnarray*}\label{VARRESVPop}
			\begin{split}
			\overline{Var}^*_{t+h|t} = \sum_{k=1}^h exp^{- 0.5k\gamma_{\eta}} \sigma^2_{\eta,t}  +  exp^{- 0.5 h \gamma_{\epsilon}} \sigma^2_{\epsilon,t} 
			\end{split} 
			\end{eqnarray*}

			\item SE: time-varying 
			\begin{eqnarray*}
		\overline {Var}^{se}_{t+h|t} = \sum^{\infty}_{\tau=0} (1-\lambda)^\tau\lambda\overline{Var}^*_{t+h|t-\tau} 
			\end{eqnarray*}

			\item NI (1-step-ahead): time-varying 
		\begin{eqnarray*}
		\overline{Var}^\theta_{t|t-1} = \overline{Var}^\theta_{t-1|t-1} + Var^*_{t|t-1}(y_t) 
		\end{eqnarray*}

		\end{itemize}
	\end{itemize}

@@

\section{Estimation}
\begin{frame}{Minimum distance estimation}

	\begin{eqnarray*}
	\widehat \Omega = \underset{\{\Omega \in \Gamma\} }{argmin} (M_{\textrm{data} } - F^{o}(\Omega, Y)) W  (M_{\textrm{data} } - F^{o}(\Omega, Y))'
	\end{eqnarray*}

	\begin{itemize}
		\item  $\Omega$: parameters of the particular $o \in \{{fire}, {se}, {ni} \} \times \{ar, sv\}$
		\item  $\Gamma$: constraints for the parameter. 
		\item $M_{data}$: data moments
		\item $F$ model moments according to a particular theory $o$, a function of parameters $\Omega$ as well as the $Y$, the real-time data (including history) up to each point of the time $t$
		\item  $W$: weight matrix, identity matrix for now 
	\end{itemize}

@@

\subsection{AR(1)}

\begin{frame}{Results: professionals and SEAR}
	\begin{figure}[ht]
		\label{SE_diag_SPF}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Results: households and SEAR}
	\begin{figure}[ht]
	\label{SE_diag_SCE}
	\begin{subfigure}[b]{0.19\textwidth}
		\centering
		\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag0.png}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.19\textwidth}
		\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag1.png}
	\end{subfigure}
\hfill
\begin{subfigure}[b]{0.19\textwidth}
	\caption{forecast/FE}
	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag2.png}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.19\textwidth}
	\caption{FE/var}
	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag3.png}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.19\textwidth}
	\caption{FE/var/Disg}
	\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_se_est_diag4.png}
\end{subfigure}
\end{figure}
\end{frame}

\begin{frame}{SE parameter estimate}
	\begin{table}
		\centering
		\caption{Minimum Distance Estimates of Parameters of SE}
		\label{GMM_Est_SE_Table}
		\begin{tabular}{lllll}
			\hline 
			0        & 1    & 2   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SCE}$(M) \\
			\hline 
			Forecast &      &     & 0.04                       & 1                          \\
			FE       &      &     & 0.05                       & 0.19                       \\
			FE       & Disg &     & 0.17                       & 0.19                       \\
			FE       & Var  &     & 0.16                       & 0.18                       \\
			FE       & Disg & Var & 0.53                       & 0.18                      \\
			\hline 
		\end{tabular}
	\end{table}
\begin{itemize}
	\item $\lambda$: update rate in SE
\end{itemize}
\end{frame}

\begin{frame}{Results: professionals and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SPF}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_ni_est_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{Results: households and NIAR}
	\begin{figure}[ht]
		\label{NI_diag_SCE}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/sce_ni_est_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}

\begin{frame}{NIAR parameters}
	\begin{table}
		\centering
		\caption{Minimum Distance Estimates of Parameters of NI}
		\label{GMM_Est_NI_Table}
		\begin{tabular}{llllll}
	\begin{tabular}{lllllll}
		\hline 
		0        & 1    & 2   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ \\
		\hline 
		Forecast &      &     & 39.65                     & 192.22                & 2.35                      & 0.38                  \\
		FE       &      &     & 12.64                     & 211.14                & 1.64                      & 0                     \\
		FE       & Disg &     & 112.37                    & 0.34                  & 512.51                    & 0.86                  \\
		FE       & Var  &     & 1.13                      & 367.43                & 0                         & 1.28                  \\
		FE       & Disg & Var & 1.29                      & 29.84                 & 2.74                      & 127.86                \\
		\hline 
	\end{tabular}  
		\end{tabular}
	\end{table}	
\begin{itemize}
	\item $\sigma_{pb}$: noisiness of public signals in NI
	\item $\sigma_{pr}$: noisiness of private signals in Ni 
\end{itemize}
\end{frame}

\subsection{Stocastic volatility}

\begin{frame}{Results: professionals and SESV}
	\begin{figure}[ht]
		\label{SESV_diag_SPF}
		\begin{subfigure}[b]{0.19\textwidth}
			\centering
			\caption{forecast}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag0.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag1.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{forecast/FE}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag2.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag3.png}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.19\textwidth}
			\caption{FE/var/Disg}
			\includegraphics[width=\textwidth, height = 0.8\textheight]{figuresDraft/spf_se_est_sv_diag4.png}
		\end{subfigure}
	\end{figure}
\end{frame}
